Pillar 1 - Sequential Pattern Mining

### 2019-03-12 Pillar 1 - Sequential Pattern Mining.Rmd
create constants in the setup section for clarity

```{r helper function}
# helper function
join_d_course     <- function(df) df %>% left_join(d_course    , by = c("Course ID"))
join_d_transcript <- function(df) df %>% left_join(d_transcript, by = c("Course ID"))

@@

For convenience:
```{r for convenience II}
course_all  <- unique(d_transactions$taken_PF_HL$item      )
student_all <- unique(d_transactions$taken_PF_HL$sequenceID)
n_students  <- length(student_all)
```

>>>>

```{r constants}
# Some old courses are present
course_all  <- unique(d_transcript$`Course ID` )
student_all <- unique(d_transcript$`Student ID`)
n_students  <- length(student_all)
```

```{r helper function}
# helper function
join_d_course     <- function(df) df %>% left_join(d_course    , by = c("Course ID")) # left_join to keep all courses present in d_transcript
join_d_transcript <- function(df) df %>% right_join(d_transcript, by = c("Course ID")) # right_joint to keep all courses present in d_transcript

@@

For convenience:
```{r for convenience II}

```
